### 2023-10-27 doc/Thesis/chapter/061-results-emma.tex
next up 063*.tex

%GENERATIONS
In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
The green points at generation number 0 indicate particles which were not included to be propagated. 
%Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
Violet lines connect individual particles in time. 
The blue line connects averages of particles of each generation (including initial non-propagated particles) and 
yellow lines connect averages of each generation of only those particles which were propagated. 
%
Both $\gamma$ and $\rho$ were to be minimized and show a clear trend towards low values with increasing generation, 
indicating that the optimization worked even though 
the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
and the chosen samples where not exactly as expected. 
Neither expected were the measurements for these samples.
The deviation from expectation might be due to high measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
Measurements were expected to show clear correlation of optimizands $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
The only statistically relevant correlation was observed for $T_{cal}$ with the optimizands.
%\td{why}
%
In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature~$T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{
		(a)~calculated conductance measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
		\td{
		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
	change colors }
		%\td{describe more in-depth in text}
	}

@@

%
% DESCRIBE COEFFICIENTS
Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ (\ref{eq:emma-phd4}) and $\hat{\gamma}$ (\ref{eq:emma-G4}); interestingly also on $\hat\lambda$ (\ref{eq:emma-layr4}) and $\hat{v}_{cal}$ (\ref{eq:emma-vcal4}).
The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$.
It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
This negative correlation could hint a compenzation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude. 
%It should be doubted, though, that the $layr$ only appears as interaction term 
%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
%
%It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
%with $T_{cal}$ and $T_{DB}$. 
%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{DB}$ only in generation 4's \gls{rf}s.
This can hint the importance of these variables in the process. 
%I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.

@@

The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimizands} for two reasons: 
Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
The process time optimization would be better placed in a follow up study. 
The second reason for including independent variables was to check if the model works. 
This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimizands} and thus 
additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
Moreover, $v_{cal}$ and $\lambda$ were only considered with 5\% weight. 
The second flaw is that there are obviously better methods to assess the quality of a model than to make it more complex. 
%Good alternatives would have been leave-one-out or cross validation.
Validation methods for sparse data include re-sampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.

>>>>

%GENERATIONS
In figures \ref{fig:emma-G-gen} and \ref{fig:emma-phd-gen} we can see the two measured main \textit{optimizands}, 
conducticity $\gamma$ and pin hole density $\rho$, of each particle at each generation.
The green points at generation number 0 indicate particles which were not included to be propagated. 
%Each violet line indicates a particle, the blue line depicts the average of all particles and the yellow line depicts the average of all particles which were propagated. 
Violet lines connect individual particles in time. 
The blue line connects averages of particles of each generation (including initial non-propagated particles) and 
yellow lines connect averages of each generation of only those particles which were propagated. 
%
Both $\gamma$ and $\rho$ were to be minimized and show a clear trend towards low values with increasing generation, 
indicating that the optimization worked even though 
the prediction functions (see equations~(\ref{eq:emma-phd3})--(\ref{eq:emma-vcal4})) 
and the chosen samples (i.e. chosen input variables) where not exactly as expected. 
Neither expected were the measurements for these samples.
The deviation from expectation might be due to measuring error of samples and variation of quality due to uncontrolled independent variables such as room temperature, humidity or solution age. 
Measurements were expected to show clear correlation of optimizands $\gamma$ and $\rho$ with mainly $c_{Zr}$ and $\lambda$.
The only statistically relevant correlation was observed for $T_{cal}$ with the optimizands.
%\td{why}
%
In the scatter plots~\ref{fig:g-tcal} and \ref{fig:phd-tcal} the correlation of calcination temperature~$T_{cal}$ with $\gamma$ and $\rho$ can be seen clearly.

\begin{figure}[hb]
    \centering
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-G.png}
        \caption{} \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/gen-phd.png}
        \caption{} \label{fig:emma-phd-gen}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/G-tcal.png}
        \caption{} \label{fig:g-tcal}
    \end{subfigure}
    \begin{subfigure}{.24\textwidth}
        \centering
        \includegraphics[width=.98\textwidth]{Pics/stats/phd-tcal.png}
        \caption{} \label{fig:phd-tcal}
    \end{subfigure}
	\caption{
		(a)~calculated conductance measures~$\gamma$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(b)~calculated pin hole density~$\rho$ of each particle against the generation number %blue shows average for each generation and yellow shows average of each generation without discarded particles from initial generation. 
		(c)~calculated conductance measures~$\gamma$ against calcination temperature $T_{cal}$
		\td{
		(d)~calculated pin hole density~$\rho$ against calcination temperature $T_{cal}$
	change colors }
	\td{increase font in gnuplot, change y-axis of (c)}
	}

@@

%
% DESCRIBE COEFFICIENTS
Furthermore, the coefficient of the $T_{cal}$ term is the largest of all terms on $\hat{\rho}$ (\ref{eq:emma-phd4}) and $\hat{\gamma}$ (\ref{eq:emma-G4}); interestingly also on $\hat\lambda$ (\ref{eq:emma-layr4}) and $\hat{v}_{cal}$ (\ref{eq:emma-vcal4}).
The coefficient of the $\lambda\cdot T_{cal}$ interaction is about a tenth in size of the $T_{cal}$ coefficient, 
but has the extra factor $\lambda$ (range: 4--12), resulting in the products of coefficients and process variables being in the same order of magnitude for $T_{cal}$ and $T_{cal}\cdot v_{cal}$ terms.
It can be noted that the coefficient of the $\lambda\cdot T_{cal}$ interaction always has contrary sign to $T_{cal}$ coefficient in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}). 
This negative correlation could hint a compenzation of the overestimated influence of $T_{cal}$ on the \textit{optimizands}.
Similarly, signs of coefficients of $\lambda \cdot T_{cal}$ and $h(\lambda -6) \cdot T_{DB}$ correlate negatively in equations~(\ref{eq:emma-phd4})--(\ref{eq:emma-vcal4}) and the product of coefficients and input variables are again similar in order of magnitude. 
%It should be doubted, though, that the $layr$ only appears as interaction term 
%together with $T_{cal}$ and $T_{DB}$, which seems rather than an artefact. 
%
%It seems rather an artefact of noise that the $\lambda$ only appears as interaction 
%with $T_{cal}$ and $T_{DB}$. 
%From the analysis of coefficients it can be said, that the most important factor according to EMMA is $T_{cal}$, followed by $\lambda$, then $T_{DB}$ and then the rest of the independent variables. 
The process variables $T_{cal}$ and $\lambda$ appear as \gls{bf}s in generation 3 and 4, whereas $v_{cal}$ only appears in generation 3's \gls{rf}s and $T_{DB}$ only in generation 4's \gls{rf}s.
This can hint the importance of these variables in the process. 
%I highly doubt though that the specific interactions proposed by EMMA are indeed meaningful.

@@

The two independent variables $v_{cal}$ and $\lambda$ were included as \textit{optimizands} for two reasons: 
Maximizing the calcination velocity and minimizing the number of layer application iterations leads to minimization of process time.
The process time optimization would be better placed in a follow up study. 
The second reason for including independent variables as \textit{optimizands} was to check if the model works. 
This idea has two flaws: there is only one set of \gls{bf}s for all \textit{optimizands} and thus 
additional dependent variables not only complicate the model but make it more difficult to predict the actual dependent variables and chose future data points. 
Moreover, $v_{cal}$ and $\lambda$ were only considered with 5\% weight in the overall objective function.
The second flaw is that there are obviously better methods to assess the quality of a model than to make it more complex. 
%Good alternatives would have been leave-one-out or cross validation.
Validation methods for sparse data include re-sampling via leave-one-out or $k$-fold cross validation\cite{kartam1997artificial}.

### 2023-10-27 doc/Thesis/chapter/062-post-emma.tex
next up 063*.tex

%WHAT CAN/DID WE TEST?
The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
We used an $\alpha$ value of 0.05 which means that 
the null hypothesis is rejected if the p-value is under 0.05. 
Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
The choice of a relatively high $alpha$-value is motivated by the rather small amount of data and low events per variable ratio.
%As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
%to guess that in 1 out of 20 cases the results could be false positives, 
%whereas the frequency is much higher. 
%A p-value of 0.01 and 0.05  mean that under the assumption that the null hypothesis is correct, 
%there is a 1\% and 5\% chance of arriving at such data as observed.
%The results should thus be taken with a grain of salt. 
%
%1 out of 20 times this result could be 
%produced by pure chance given that the null hypothesis is true. 
%If the p-value is below that value, then we choose to accept, that the data is not due to
%chance but due to the influence of the independent variables on the dependent variables. 
%\td{could test anova on different generations data sets}

@@

%
Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $\lambda$ themselves -- are the smallest among the input variables. 
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
In order to compare, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{min}+x_{max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
The biggest influence on $\hat\rho$ is  $\lambda$, followed by $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artefact of the noise rather than a process property. 
%Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
%Different distributions were not expected. 
The two very different distributions of influence among the input variables can have three reasons:
%This can have two reasons: 
(1) the linear function is not a suitable regression function for the data distribution.
(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
(3) the \textit{optimizands} indeed represent different properties of the material.
%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Grid Search, KRR and SVM}
The optimal parameters for each combination of 
\textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took the smallest possible value (within the grid search) twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
So, 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters (stimulate regularization and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{cccccccc}
        \hline\hline
        method  &$R^2$   &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$) & $-0.50 \pm 0.25$  &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $) & $-0.45 \pm 0.52$  &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$) & $-0.37 \pm 0.39$  &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $) & $-0.95 \pm 0.44$  &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{$R^2$ values and best hyperparameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$.

@@

%
Finally, the \gls{mae} and \gls{mse} were calculated for different data sets 
(see table \ref{tab:post-emma}). 
Each models was trained on the \gls{emma} data set.
% EMMA 30 pts
The first two columns (e) show statistics validated with data the model was trained with (30 data points) and thus, 
these columns contain the lowest numbers. 
% pre-EMMA 21 pts 
The next two columns (p) were calculated with data obtained before the EMMA optimization (21 data points). 
As the pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
many data points are outside of the range of the \gls{emma} data set. 
Thus, prediction for this data set are mainly extrapolations. 
It must be explicitly noted at this point that pre-EMMA samples differ from EMMA samples 
in the stabilization agent and therefore might underperform. 
% inter/c/ pre-EMMA 5 pts
The next two columns (c) were produced by using pre-\gls{emma} data for validation, 
but only keeping points which sit inside the space spanned by the \gls{emma} constraints (5 data points). 
It should be expected that these statistics should be lower than in the previous two columns. 
They are only lower for MARS($\rho$) and LR($\rho$), though. 
This is likely due to the small sample size.
% all 51 
The last two columns show data for predictions of all available data (51 data points). 
These statistics are lower because of the inclusion of the training set in the test set.

>>>>

%WHAT CAN/DID WE TEST?
The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
We used an $\alpha$-value of 0.05 which means that 
the null hypothesis is rejected if the p-value is under 0.05. 
Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
The choice of a relatively high $alpha$-value is motivated by the rather small amount of data and low events per variable ratio.
%As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
%to guess that in 1 out of 20 cases the results could be false positives, 
%whereas the frequency is much higher. 
%A p-value of 0.01 and 0.05  mean that under the assumption that the null hypothesis is correct, 
%there is a 1\% and 5\% chance of arriving at such data as observed.
%The results should thus be taken with a grain of salt. 
%
%1 out of 20 times this result could be 
%produced by pure chance given that the null hypothesis is true. 
%If the p-value is below that value, then we choose to accept, that the data is not due to
%chance but due to the influence of the independent variables on the dependent variables. 
%\td{could test anova on different generations data sets}

@@

%
Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $\lambda$ themselves -- are the smallest among the input variables. 
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
For better comparison, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{i,min}+x_{i,max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
The biggest influence on $\hat\rho$ is  $\lambda$, followed by $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artefact of the noise rather than a process property. 
%Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
%Different distributions were not expected. 
The two very different distributions of influence among the input variables can have three reasons:
%This can have two reasons: 
(1) the linear function is not a suitable regression function for the data distribution.
(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
(3) the \textit{optimizands} indeed represent different properties of the material.
%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Grid Search, KRR and SVM}
The optimal parameters for each combination of 
\textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took the smallest possible value (within the grid search) twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ (see section~\ref{sec:ml-methods}) was 0.01--10 in the grid search. 
So, 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{cccccccc}
        \hline\hline
        method  &$R^2$   &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$) & $-0.50 \pm 0.25$  &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $) & $-0.45 \pm 0.52$  &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$) & $-0.37 \pm 0.39$  &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $) & $-0.95 \pm 0.44$  &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{$R^2$ values and best hyperparameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$. 
\td{how can R2 be below zero?}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score

@@

%
Finally, the \gls{mae} and \gls{mse} were calculated for different data sets 
(see table \ref{tab:post-emma}). 
Each models was trained on the \gls{emma} data set.
% EMMA 30 pts
The first two columns ((e)) show statistics validated with data the model was trained with (30 data points) and thus, 
these columns contain the lowest numbers. 
% pre-EMMA 21 pts 
The next two columns (p) were calculated with data obtained before the EMMA optimization (21 data points). 
As the pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
many data points are outside of the range of the \gls{emma} data set. 
Thus, predictions for this data set are mainly extrapolations. 
It must be explicitly noted at this point that pre-EMMA samples differ from EMMA samples 
in the stabilization agent and therefore might deviate even more. 
% inter/c/ pre-EMMA 5 pts
The next two columns (c) were produced by using pre-\gls{emma} data for validation, 
but only keeping points which sit inside the space spanned by the \gls{emma} constraints (5 data points). 
It should be expected that these statistics should be lower than in the previous two columns. 
They are only lower for MARS($\rho$) and LR($\rho$), though. 
This is likely due to the small sample size.
% all 51 
The last two columns show data for predictions of all available data (51 data points). 
These statistics are lower than the middle columns because of the inclusion of the training set in the test set.

### 2023-10-27 doc/Thesis/chapter/063-discussion.tex
corrected until comp details
next up 063*.tex

\section{Hindsight is easier than foresight}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: zation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned from each phase of this project. % in chronological order. 
Firstly,
the \nameref{sec:phase1} will be discussed in subsection \ref{sec:phase1}, 
followed by the \nameref{sec:phase2} reviewd in subsection \ref{sec:phase2} 
%, thereupon the 
and finally the \nameref{sec:phase3} examined in subsection \ref{sec:phase3}.
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
% will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. 
I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that 
improving the recipe still lead to poor performance.
%no matter how much I improved it, it was still bad. 
This was only noticed this after trying out another recipe. 
The author's tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever can be. 
This will 
make it possible to acquire 
%get you a 
``feel'' of what works and what does not. 
%Thinking back to some design classes I took with \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir} for data visualization: 
This is inspired by a quote from \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir}'s 
data visualization classes: ``create as many and different designs as possible''.
One should check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.

>>>>

\section{Hindsight is easier than foresight}
\label{sec:res-discussion}
%\section{Discussion}
%\todo{search i.e. and replace with i.e.\ }
%\todo{go to experimental and material (IV) discussion}
%\td{I-V: 2 terminal measurement one terminal was varibale and the other the ground from $-5*10^{-3}$ V to $5*10^{-3}$ V with steps of $10^{-2}$ measure current from back bone to backbone if shorted, then can measure actual resistance of layer. resistance of steel is neglectable. In order to get an impression of the quality of the layer mutliple contact (picture) are sputtered (throuhg a mask) and statistics: Two angabewerte: the weighted durchschnit and the number of pinholes, ie the number of contacts which were shorted, have an resistance below an threshold. if tunneling, iv follows powerlaw, if direct contact, iv follows linear }
%\todo{go to anova discussion}
%- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
%\todo{british or US?: zation vs zation} 
%\todo{ include last phase into previous section}
This section will discuss mistakes, improvements and lessons learned from each phase of this project. % in chronological order. 
Firstly,
the "\nameref{sec:phase1}" will be discussed in subsection \ref{sec:phase1}, 
followed by the "\nameref{sec:phase2}" reviewd in subsection \ref{sec:phase2} 
%, thereupon the 
and finally the "\nameref{sec:phase3}" examined in subsection \ref{sec:phase3}.
%\ref{sec:phase3} \textit{\nameref{sec:phase4}}%
% will be discussed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research, exploration and design phase}
\label{sec:phase1}
%\td{freewriting}: 
\textbf{Scrutinize everything!} At the beginning of a project it is important 
to get a ``feel''. 
I took the first recipe as only true recipe and tried to tune it to perfection. 
The problem was that the base line of that recipe was so low such that 
improving the recipe still lead to poor performance.
%no matter how much I improved it, it was still bad. 
This was only noticed after trying out another recipe. 
The author's tip here is to read as much and mostly diverse literature as possible and then try to mimic what ever can be. 
This will 
make it possible to acquire 
%get you a 
``feel'' of what works and what does not. 
%Thinking back to some design classes I took with \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir} for data visualization: 
This is inspired by a quote from \href{http://www.tomtorsneyweir.com/}{Thomas Torsney-Weir}'s 
data visualization classes: ``create as many and different designs as possible''.
One should check what works, collect (dis-)advantages of methods and combine the best approaches. 
This can save you a lot of time.
